### 2009-04-06 talk/icooolps2009-dotnet/clibackend.tex
fix another XXX, and some other small fixes

Unfortunately, the CLI VM does not allow modification of code which
has been already loaded and linked, therefore the simplest approach
taken for low level architectures does not work for higher level 
virtual machines as those for .NET and Java.

>>>>

Unfortunately, the CLI VM does not allow modification of code which
has been already loaded and linked, therefore the simplest approach
taken for low level architectures does not work.
